TBD

### 2024-04-07 outputs/paper/paper.qmd
paper updated

# read in data
file_path_0 <- "../../inputs/data/cali_house_price.csv"
file_path_1 <- "../../outputs/data/cali_house_price_clean.csv"
file_path_2 <- "../../outputs/data/ocean_proximity_frequency.csv"
file_path_3 <- "../../outputs/data/.csv"

cali_house_price <- read_csv(file_path_0, show_col_types = FALSE)
cali_house_price_clean<- read_csv(file_path_1, show_col_types = FALSE)
ocean_proximity_frequency<- read_csv(file_path_2, show_col_types = FALSE)

@@

longitude_summary <- summary(cali_house_price %>% select(longitude))
latitude_summary <- summary(cali_house_price %>% select(latitude))
housing_median_age_summary <- summary(cali_house_price %>% select(housing_median_age))
total_rooms_summary <- summary(cali_house_price %>% select(total_rooms))
total_bedrooms_summary <- summary(cali_house_price %>% select(total_bedrooms))
population_summary <- summary(cali_house_price %>% select(population))
households_summary <- summary(cali_house_price %>% select(households))
median_income_summary <- summary(cali_house_price %>% select(median_income))
median_house_value_summary <- summary(cali_house_price %>% select(median_house_value))

kable(longitude_summary)
kable(latitude_summary)
kable(housing_median_age_summary)
kable(total_rooms_summary)
kable(total_bedrooms_summary)
kable(population_summary)
kable(households_summary)
kable(median_income_summary)
kable(median_house_value_summary)

@@

null_values <- cali_house_price %>%
  summarise_all(~sum(is.na(.))) %>%
  gather(key = "Variables", value = "MissingValues")

kable(null_values)
```

@@

null_values <- cali_house_price_clean %>%
  summarise_all(~sum(is.na(.))) %>%
  gather(key = "Variables", value = "MissingValues")

kable(null_values)
```

@@

ggplot(ocean_proximity_frequency, aes(x = Variable, y = Frequency)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Frequency of Categories in Ocean Proximity",
       x = "Ocean Proximity",
       y = "Frequency") +
  coord_flip()

@@

>>>>

# read in data
state_house_price_by_year <- read_csv("outputs/data/state_house_price_by_year.csv")
state_house_price_by_month <- read_csv("outputs/data/state_house_price_by_month.csv")

state_1b_house_price_by_year <- read_csv("outputs/data/state_1b_house_price_by_year.csv")
state_2b_house_price_by_year <- read_csv("outputs/data/state_2b_house_price_by_year.csv")
state_3b_house_price_by_year <- read_csv("outputs/data/state_3b_house_price_by_year.csv")
state_4b_house_price_by_year <- read_csv("outputs/data/state_4b_house_price_by_year.csv")
state_5bplus_house_price_by_year <- read_csv("outputs/data/state_5bplus_house_price_by_year.csv")

state_1b_house_price_by_month <- read_csv("outputs/data/state_1b_house_price_by_month.csv")
state_2b_house_price_by_month <- read_csv("outputs/data/state_2b_house_price_by_month.csv")
state_3b_house_price_by_month <- read_csv("outputs/data/state_3b_house_price_by_month.csv")
state_4b_house_price_by_month <- read_csv("outputs/data/state_4b_house_price_by_month.csv")
state_5bplus_house_price_by_month <- read_csv("outputs/data/state_5bplus_house_price_by_month.csv")

@@

@@

@@

@@

@@

library(maps)
library(dplyr)
library(readr)
library(viridis)
library(ggplot2)
